Suppl. Figure 5. Rarefaction curves

### 2022-10-11 reports/manuscript/Suppl.Figure4-5.Rmd
change name

---
title: "Suppl. Figure 3. & 4. Mirobiome-KEGG correlations."
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/SupplFigure3_4/", ...)
    })
---

@@

#########
# PATHS #
#########
PATH <- "../../.."
reprod_files <- "../../data/reprod.Suppl.Fig.3_4/"

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
SNN_bacteria <- read.csv("../../results/04_clustering_output/bacteria_SNN_graph.csv",row.names = 1)
# setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
#datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")
#SNN_bacteria <- read.csv("../../../results/bacteria_SNN_graph.csv",row.names = 1)
bac_communities <- read.xlsx("./Suppl.Tbl/Suppl.Tbl.01.xlsx", sheet = "Bacterial Communities")

@@

# ASV <- list(c("Luminal","ASV_CVL_V3_normalized_batch_corrected"),
#             c("Tissue","ASV_tissue_V3_normalized_batch_corrected")
#             )
ASV <- list(c("Luminal","ASV_Luminal_normalized"),
            c("Tissue","ASV_Tissue_normalized")
            )
# i <- ASV[[1]]
for(i in ASV){
  cat(paste0("Correlation between RNAseq and ",i[1], " 16S","\n"))

>>>>

---
title: "Suppl. Figure 3. & 4. Mirobiome-KEGG correlations."
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/SupplFigure4_5/", ...)
    })
---

@@

#########
# PATHS #
#########
PATH <- "../../.."
reprod_files <- "../../data/reprod.Suppl.Fig.4_5/"

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../results/03_normalize_data_output/datasets_all_samples.RDS")
SNN_bacteria <- read.csv("../../results/04_clustering_output/bacteria_SNN_graph.csv",row.names = 1)
bac_communities <- read.xlsx("./Suppl.Tbl/Suppl.Tbl.01.xlsx", sheet = "Bacterial Communities")

@@

ASV <- list(c("Luminal","ASV_Luminal_normalized"),
            c("Tissue","ASV_Tissue_normalized")
            )
# i <- ASV[[1]]
for(i in ASV){
  cat(paste0("Correlation between RNAseq and ",i[1], " 16S","\n"))

### 2022-10-11 reports/manuscript/Suppl.Figure6.Rmd
change name

---
title: "Suppl. Figure 5. Rarefaction curves"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/SupplFigure5/", ...)
    })
---

@@

#############
# LODA DATA #
#############
paths_p <- c('../../../data/phyloseq_boston_r1.RDS',   # CVL V3 (2 replicates of one tissue + 27 CVL V2)
             '../../../data/phyloseq_boston_r2.RDS',   # Tissue V3 & CVL V2
             '../../../data/phyloseq_Sthlm.RDS'        # CVL V2, (only v4 region)
             )

>>>>

---
title: "Suppl. Figure 5. Rarefaction curves"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/SupplFigure6/", ...)
    })
---

@@

#############
# LODA DATA #
#############
paths_p <- c('../../data/phyloseq_boston_r1.RDS',   # CVL V3 (2 replicates of one tissue + 27 CVL V2)
             '../../data/phyloseq_boston_r2.RDS',   # Tissue V3 & CVL V2
             '../../data/phyloseq_Sthlm.RDS'        # CVL V2, (only v4 region)
             )
